Optimal (Multiway) Spatial Joins

### 2024-05-28 msj.tex
yufei

\extraspacing {\underline{\em Example 5.4.}} For $\bm{t}_1 = (\alpha, h_2', v_1)$, first find the full segment of $h_2'$, which is $h_2$. As $\beta_1$ is the only rectangle in $\contained_{R_2}(\bm{t}_1)$, Line 5 adds tuple $(\alpha, \beta_1, h_2, v_1)$ to $\J_2$. For $\bm{t}_2 = (\alpha, h_3', v_2)$, the full segment of $h_3'$ is $h_3$. As $\contained_{R_2}(\bm{t}_2) = \set{\beta_1, \beta_2, \beta_3}$, Line 5 adds $(\alpha, \beta_1, h_3, v_2)$, $(\alpha, \beta_2, h_3, v_2)$, and $(\alpha, \beta_3, h_3, v_2)$ to $\J_2$. Finally, the processing of $\tm{t}_3 = (\alpha, h_3', v_2)$ adds $(\alpha, \beta_3, h_3, v_2)$ to $\J_2$.
\qed

@@

>>>>

\extraspacing {\underline{\em Example 5.4.}} For $\bm{t}_1 = (\alpha, h_2', v_1)$, first find the full segment of $h_2'$, which is $h_2$. As $\beta_1$ is the only rectangle in $\contained_{R_2}(\bm{t}_1)$, Line 5 adds tuple $(\alpha, \beta_1, h_2, v_1)$ to $\J_2$. For $\bm{t}_2 = (\alpha, h_3', v_1)$, the full segment of $h_3'$ is $h_3$. As $\contained_{R_2}(\bm{t}_2) = \set{\beta_1, \beta_2, \beta_3}$, Line 5 adds $(\alpha, \beta_1, h_3, v_1)$, $(\alpha, \beta_2, h_3, v_1)$, and $(\alpha, \beta_3, h_3, v_1)$ to $\J_2$. Finally, the processing of $\bm{t}_3 = (\alpha, h_3', v_2)$ adds $(\alpha, \beta_3, h_3, v_2)$ to $\J_2$.
\qed

@@

\extraspacing {\underline{\em Example 5.5.}} As mentioned $\J(R_1, H', V)$ has 3 tuples $\bm{t}_1$, $\bm{t}_2$, and $\bm{t}_3$. Both $\bm{t}_2 = (\alpha, h_3', v_2)$ and $\bm{t}_3 = (\alpha, h_3', v_2)$ have $h_3'$ as the horizontal segment. Therefore, $\minleft(h_3')$ equals the smaller between the x-coordinate of $v_1$ and that of $v_2$. The minimal segment $h_3^*$ of $h_3'$ is shown in Figure~\ref{fig:hv:type2:ex}(c). On the other hand, it is easy to verify that $\minleft(h_2')$ is the x-coordinate of $v_1$. The minimal segment $h_2^*$ of $h_2'$ is also shown in Figure~\ref{fig:hv:type2:ex}(c).
\qed
